---
pagetitle: "American Psychology-Law Society"
page-layout: custom
section-divs: false
toc: false
description: |
  The American Psychology-Law Society (AP-LS), Division 41 of the American Psychological Association is an organization dedicated to enhancing the well-being, justice, and human rights through the science and practice of psychology in legal contexts.  
search: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("assets/apls_functions.R")
```



::: {#hero-banner .column-screen}
::: {.grid .column-page}

:::


```{r}
#| classes: '.g-col-lg-6 .g-col-12 .g-col-md-12'
#| echo: false
#| warning: false
#| message: false
carousel("gallery-carousel", 5000, 
         yaml.load_file("carousel.yml"))
```

:::

::: {#gallery .column-page}
:::

```{=html}
<style>
#hero-banner {
  padding-top: 35px;
  padding-bottom: 20px;
  
}
#quarto-content main { 
  margin-top: 0;
  padding-top: 0;
}
html {
  scroll-behavior: smooth;
}
.headline {
font-size: 1.25em;
font-weight: 300;
padding-bottom: 1em;
}
.headline p {
  margin: 25px;
  padding-bottom: 0.2rem;
}
.headline a {
  text-decoration: none;
}
.headline ul li {
  margin-bottom: 0.3em;
}
.carousel.card {
  padding-top: 2em;
}
.carousel img {
  width: 70%;
  margin-bottom: 110px;
}
.carousel-control-prev-icon, .carousel-control-next-icon {
  margin-bottom: 110px;
}
.carousel-caption {
  padding-top: 1em;
  padding-bottom: 1em;
}
.touch {
  
}
</style>
```
::: vspace
:::

::: {.column-screen .light-section}
::: grid
```{r}
#| label: Row of links
#| echo: false
#| warning: false
#| message: false
content = rowwise_table(~name, ~icon, ~link,
                        "About", "info-circle-fill", "about/about.html",
  "Committees", "person-rolodex", "about/committees.html",
    "Conference", "easel2-fill", "conferences/index.html", 
    "Funding", "award-fill", "awards/index.html",
    "Students", "mortarboard-fill", "https://www.apls-students.org/resources.html"
  
)
div(class = "bg-light",
 div(class = "bg-breakout",
    div(class = "inner-container",
      div(class = "boxed-wrapper",
            div(class = "boxed-feature-grid",
          pmap(content, function(name, icon, link) {
            div(class = "boxed-feature-grid__item",
              div(class = "boxed-feature-grid__icon",
                a(href = link, class = "boxed-feature-grid__link",
                  tags$i(class = sprintf("bi-%s boxed-feature-grid__i", icon))
                )),
    div(class = "boxed-feature-grid__title", name)
)
          })
        )
      )
    )
  )
)

```
:::
:::

```{r}
#| label: Membership info-bar 
#| output: asis
#| echo: false
#| warning: false
#| message: false

info <- tibble(
  title = "Interested in AP-LS?",
  text = "Become a member.",
  ctr = "Join now",
  link = "membership/membership.qmd",
  icon = "fas fa-scale-balanced"
)

html <- generate_info_bar(info)

cat(html)

```

::: vspace
:::

::: {.column .col-v-center width="15%"}
:::

::: {.column .col-v-center width="70%"}
```{r}
#| echo: false
profile_circle_preview <- '
<div class="p-3 text-center rounded-circle m-3 shadow-lg" style="background-size: cover; background-image: url({image}); width: 225px; height: 225px">
<div class="visually-hidden">{alt}</div>
</div>'
profiles_cropped <- list(
  image = "about/presidents/daniel_murrie.jpg",
  alt = c(
    "Picture of Daniel Murrie"
  )
)
profiles_cropped_html <- glue::glue_data(profiles_cropped, profile_circle_preview)
profiles_cropped_html <- htmltools::HTML(profiles_cropped_html)
```

::: portrait
`r profiles_cropped_html`
:::


# Welcome from Our President
::: vspace
:::

::: president-intro
<p>Welcome to the American Psychology-Law Society (AP-LS), Division 41 of the American Psychological Association.</p>

<p>Our organizational mission is to "enhance well-being, justice, and human rights through the science and practice of psychology in legal contexts". AP-LS is the premiere organization for students and professionals who are interested in issues at the intersection of psychology and law.</p>

<p>As an organization, we strive to support our members in their work using psychological science and practice to advance justice in our legal system.</p>
:::

::: about-link
[MORE FROM THE PRESIDENT](about/presidents/index.html)
:::
:::

::: {.simple-info-blue .alt-background-blue}
::: content-block-blue
### Get ready for the 2024 American Psychology-Law Society Conference!

Los Angeles, CA---March 21-23

[Learn more{{< fa arrow-right >}}](conferences/index.html){.btn-action .btn .btn-secondary .btn-lg role="button"}
:::
:::

::: {.column-screen .light-section}
::: grid
```{r}
#| label: Row of sub-links
#| echo: false
#| warning: false
#| message: false
content = rowwise_table(~name, ~icon, ~link,
                        "Contact", "chat-dots", "about/contact.html",
  "Newsletter", "newspaper", "resources/newsletter/index.html",
    "Job Posts", "briefcase-fill", "resources/job_postings/index.html", 
    "APA", "award-fill", "https://convention.apa.org/future-conventions",
    "Videos", "play-circle", "resources/videos/index.html"
)
div(class = "bg-light",
 div(class = "bg-breakout",
    div(class = "inner-container",
      div(class = "boxed-wrapper",
            div(class = "boxed-feature-grid",
          pmap(content, function(name, icon, link) {
            div(class = "boxed-feature-grid__item",
              div(class = "boxed-feature-grid__icon",
                a(href = link, class = "boxed-feature-grid__link",
                  tags$i(class = sprintf("bi-%s boxed-feature-grid__i", icon))
                )),
    div(class = "boxed-feature-grid__title", name)
)
          })
        )
      )
    )
  )
)

```
:::
:::
