---
sidebar: true
toc: false
page-layout: article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../_site/apls_functions.R")
```



```{r}
#| include: false
#| echo: false

resource_grid = function(content) {
  div(class = "grid grid-three",
    pmap(content, function(category, name, icon, url, text) {
      div(class = "grid__item",
        h3(class = "grid__title",
          tags$i(class = sprintf("bi-%s grid__title-icon", icon)),
          HTML("&nbsp;"),
          name
        ),
        p(
        paste0(text, "."),
        a(href = url, "aria-label" = sprintf("Go to %s", name), span(class = "grid__link-box"))
        )
      )
    })
  )
}
# Text description should be one sentence
content = rowwise_table(
  ~category, ~name, ~icon, ~url, ~text,
  "general", "Job postings", "briefcase", "job_postings/index.qmd", "List of job opportunities related to law-psychology",
  "general", "AP-LS eNewsletter", "newspaper", "newsletter/", "Collection of case studies and demos",
  "general", "Student Resources", "question-circle", "https://www.apls-students.org/resources.html", "Collection of information for students",
  "general", "AP-LS Videos", "file-earmark-play", "talks/index.qmd", "Collection of webinars, talks and videos.",
  "general", "Syllabi Collection", "table", "syllabi/index.qmd", "Collection of syllabi for courses related to psychology and law.",
  "general", "Telepsychology", "telephone", "telepsychology/telepsychology.qmd", "Collection of articles and resources about telepsychology",
  "general", "Reports", "folder", "reports/index.qmd", "Access reports by AP-LS committees and taskforces.", "general", "Books", "book", "", "Find books on psychology and law topics.",
  "general", "Forensic Guidelines", "file-earmark-ruled", "guidelines/index.qmd", "Specialty Guidelines for Forensic Psychologists from APA")
setkeyv(content, "category")
```



## Resources 

Stay up to date with the activities of AP-LS and its members.

```{r, echo = FALSE}
resource_grid(content[.("general")])
```


## Job Postings
```{=html}
<div class="gallery">
  <div class="gallery__icon-column">
      <i class="fa-solid fa-business-time fa-3x" title="Briefcase with clock" aria-hidden="true"></i>
  </div>
  <div class="gallery__list-column">
```

::: {#jobs}
:::

::: {.all-link}
[See all posts](jobs/)
:::

## Teaching Psychology & Law

```{=html}
<div class="gallery">
  <div class="gallery__icon-column">
      <i class="fa-solid fa-chalkboard-user fa-3x" title="Person at chalkboard" aria-hidden="true"></i>
  </div>
  <div class="gallery__list-column">
```

::: {#teaching}
:::
Syllabus Collection: The AP-LS Teaching, Training, and Careers Committee is continuing its efforts to collect syllabi for courses in Psychology and Law or closely related topics. You may download any of the collected syllabi for undergraduate or graduate courses."Activities for Teaching Psychology and Law: A Guide for Instructors" by Zelechoski, Wolbransky, and Riggs Romaine, offers a wide variety of such activities for courses in psychology and law. The activities incorporate individual and group work, videos, reading materials, classroom discussions, homework assignments, and lots of interactive exercises.Teaching Materials for Undergraduate Legal Psychology Courses: Dr. Edie Greene and Erica Drew have collected information intended for instructors of undergraduate courses in psychology and law. Download "Resources for Teaching Undergraduate Psychology and Law Courses" (PDF, 416KB)
View list of other available resources for those teaching courses in psychology and law.

::: {.all-link}
[see more](teaching/)
:::

## Reports
```{=html}
<div class="gallery">
  <div class="gallery__icon-column">
      <i class="fa-solid fa-folder fa-3x" title="File" aria-hidden="true"></i>
  </div>
  <div class="gallery__list-column">
```

::: {#reports}
:::

::: {.all-link}
[more reports](reports/)
:::

## AP-LS Videos
```{=html}
<div class="gallery">
  <div class="gallery__icon-column">
      <i class="fa-solid fa-file-video fa-4x" title="Video file" aria-hidden="true"></i>
  </div>
  <div class="gallery__list-column">
```

:::{#talks}
:::

::: {.all-link}
[more videos](talks/)
:::




## Education and Training in Psychology and Law
```{=html}
<div class="gallery">
  <div class="gallery__icon-column">
      <i class="fa-solid fa-newspaper fa-3x" title="Newsletter" aria-hidden="true"></i>
  </div>
  <div class="gallery__list-column">
```

::: {#education}
:::
One goal of AP-LS is promoting the education of psychologists in matters of law and the education of legal personnel in matters of psychology. Information about pursuing a career in psychology and law can be found here. You can also learn more about the field through our interviews with professionals’ series. This page summarizes our ongoing educational activities.

### Graduate Programs
There are over 50 doctoral and master's programs that teach a combination of psychology and law. Information about, and links to, these programs can be found on the page about graduate programs.

Members of the Teaching, Training, and Careers Committee (TTC) developed a guide to assist students interested in psychology and law graduate programs.The Resource Directory of Forensic Psychology Predoctoral Internships Training Programs includes a listing of predoctoral internships offering training opportunities in forensic psychology.The Education and Training Guidelines (PDF, 52KB), developed by the Forensic Specialty Council of the Council of Specialties in Professional Psychology, outline the required elements of an organized, sequential training program in forensic psychology, including postdoctoral residency training.

```{=html}
  <span class="gallery__link">
    <a href="gallery-all.html">View more <i class="bi-arrow-right-short"> </i></a>
  </span>
  </div>
</div>
```


