---
title: Caregiving Grants for American Psychology-Law Conference
date: last-modified
description: Provides travel awards to APLS members who serve as a caregiver in any capacity (e.g., child, parent) to attend the American Psychology-Law Society Conference.
categories: 
  - Students
  - Undergraduate
  - Graduate
  - Diversity, Equity & Inclusion
  - Conference Travel
  - Early Career Professionals
  - Caregiving Grants
submission-info:
  sponsor: AP-LS Professional Development of Women Committee
  deadline: January 27, 2023
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../../_site/apls_functions.R")
```

::: vspace
:::

::: callout-note
# 2023 Conference
The AP-LS Professional Development of Women Committee is thrilled to offer Caregiving Grants of $500-$750 for 20-30 attendees of APLS 2023 in Philadelphia, with priority to first authors, presenters, students, and early career professionals. This grant is open to any APLS member (student and non-student) who serves as a caregiver in any capacity (e.g., child, parent). Funds can be used for any caregiving needs during the conference, including needs at the conference or at home.

 
We will notify grantees by February 3, 2023. 
```{r}
#| echo: false
#| output: asis

library(tibble)
library(dplyr)

# Important links for award
links <- tibble(
  icon = c("circle-info", "envelope", "link"),
  text = c("About PDW Committee", "Contact", "Link to Apply"),
  url = c("../../about/committees.qmd", "mailto:Jennifer.m.cox@ua.edu", "https://universityofalabama.az1.qualtrics.com/jfe/form/SV_4Jilv1WU81DVrGm")
)

# Create inline objects for each row of the tibble
inline_objects <- lapply(seq_len(nrow(links)), function(i) {
  create_inline_object(links[i, "icon"], links[i, "text"], links[i, "url"])
})

# Combine the inline object strings into a single string
inline_objects_str <- paste(inline_objects, collapse = "")

# Print the HTML string
cat(inline_objects_str)
```
:::
