---
title: Student Presentation Awards for American Psychology-Law Conference
date: last-modified
description: Provides awards to students presenting their work at the American Psychology-Law Society Conference.
categories: 
  - Students
  - Undergraduate
  - Graduate
  - Conference Travel
submission-info:
  sponsor: AP-LS Student Committee
  deadline: "February 22, `r format(Sys.Date(), '%Y')`"
links:
- icon: info-circle
  name: Learn More
  url: "http://www.apls-students.org/student-presentation-awards1.html"
- icon: send
  name: Apply here
  url: "https://docs.google.com/forms/d/e/1FAIpQLSe80sfriAr71KEVvaj5CSVmR-UALYeB04ewjvv8M1NaBsjNIQ/viewform"
- icon: envelope-at
  name: Contact
  url: "mailto:aplsstudents@gmail.com"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../../assets/apls_functions.R")
```

::: vspace
:::

::: callout-note
# `r format(Sys.Date(), '%Y')` American Psychology-Law Conference

Student members with an accepted first author presentation for the `r format(Sys.Date(), '%Y')` AP-LS Conference are eligible and highly encouraged to apply for a Student Presentation Award.

The AP-LS Student Committee will be awarding ten (10) student presentation awards at the `r format(Sys.Date(), '%Y')` AP-LS Conference, totaling \$1,750. These awards include:

-   Two (2) Outstanding Student Paper awards (\$200 each);

-   Two (2) Outstanding Student Abbreviated Paper ("Data Blitz") awards (\$175 each);

-   Two (2) Outstanding Student Poster awards (\$150 each); and

-   Four (4) specialty awards, which can be posters, abbreviated papers, or papers.

These include:

-   One (1) Outstanding Student Presentation in Diversity-Related Research award (\$175), for research directly related to underrepresented or marginalized populations.

-   One (1) Outstanding Student Presentation in Corrections Research award (\$175), for research directly related to correctional settings.

-   One (1) Outstanding Student Presentation in Legal Research award (\$175), for research directly related to the law or legal practice.

-   One (1) Outstanding Student Presentation in Novel-Topic Research award (\$175), for research on a topic not traditionally studied in law and psychology.

    Full information on submission criteria, submission instructions, and the evaluation process is available on the [student committee website](https://www.apls-students.org/student-presentation-awards1.html).

Completed submissions are due on the date of the deadline by 11:59 PM EST. Late or incomplete submissions will not be considered.

```{r}
#| echo: false
#| output: asis

library(tibble)
library(dplyr)

# Important links for award
links <- tibble(
  icon = c("circle-info", "envelope", "link"),
  text = c("About Student Committee", "Contact", "Student Website"),
  url = c("../../about/committees.qmd", "mailto:students@ap-ls.org", "https://www.apls-students.org/student-presentation-awards1.html")
)

# Create inline objects for each row of the tibble
inline_objects <- lapply(seq_len(nrow(links)), function(i) {
  create_inline_object(links[i, "icon"], links[i, "text"], links[i, "url"])
})

# Combine the inline object strings into a single string
inline_objects_str <- paste(inline_objects, collapse = "")

# Print the HTML string
cat(inline_objects_str)
```
:::
