---
title: "About"
subtitle: Welcome to the American Psychology-Law Society 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../_site/apls_functions.R")
```

## Welcome to the American Psychology-Law Society (AP-LS)

### We are Division 41 of the American Psychological Association. 

AP-LS members and the organization itself work to advance the contributions of psychology to the understanding of law and legal institutions through basic and applied research; promote the education of psychologists in matters of law and the education of legal personnel in matters of psychology, including the appropriate use of psychologists in the legal system; and inform the psychological and legal communities and the general public of current research, educational and service activities in the field of psychology and law.

We enhance well-being, justice, and human rights through the science and practice of psychology in legal contexts.

## Our Mission

The American Psychology-Law Society outlines three goals that reflect the many activities, specialties, and contributions made by our members:

- Advancing the contributions of psychology to the understanding of law and legal institutions through basic and applied research.

- Promoting the education of psychologists in matters of law and the education of legal personnel in matters of psychology.

- Informing the psychological and legal communities and the general public of current research, educational and service activities in the field of psychology and law.

## Core Values

The American Psychology-Law Society commits to its vision through a mission based upon the following values:

```{r}
#| echo: false
#| message: false
#| warning: false
#| classes: '.g-col-lg-6 .g-col-12 .g-col-md-12'

content = rowwise_table(~icon, ~text, ~link,
          "award-fill",
            "Continual pursuit of excellence", 
              "",
          "clipboard2-data",          
            "Knowledge and application based on methods of science",
              "",
          "people-fill",          
            "Outstanding service to its members",
              "",
          "megaphone",      
            "Social justice, diversity, and inclusion",              
              "",
          "signpost-split",        
            "Ethical action in all that we do",                   
              "",
          "globe",
            "Outstanding service to society",
              ""
)
div(class = "feature-grid",
  pmap(content, function(icon, text, link) {
    div(class = "feature-grid__item",
        div(class="feature-grid__icon",
          a(href = link, class = "feature-grid__link",
            tags$i(class = sprintf("bi-%s feature-grid__i", icon))
         )
       ),
      text
    )
  })
)
```

## Vision Statement

The American Psychology-Law Society aspires to excel as a valuable, effective and influential organization advancing the science of psychology-law and the translation of psychology-law knowledge into practice and policy, serving as:

**A uniting force** for psychology-law science and practice.

**The major catalyst** for the stimulation, growth and dissemination of psychology-law science and practice.

**The primary resource** for all psychology-law scholars and practitioners and for members of other disciplines with interests in psychology-law science and practice.

**The premier innovator** in the education, development, and training of psychology-law scientists, practitioners and educators.

**The leading advocate** for psychology-law knowledge and practice informing practitioners, policy makers and the public to use psychology-law knowledge in the pursuit of justice for all citizens.

**A principal leader** and global partner promoting psychology-law knowledge and methods to improve justice in diverse, multicultural and international contexts.

**An effective champion** of the application of psychology-law to promote human rights, dignity, and justice.