---
title: "Membership"
description: |
  AP-LS membership is for the calendar year January 1 - December 31.
toc: false
section-divs: false
title-block-banner: "files/default-banner.svg"
link-external-icon: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../assets/apls_functions.R")
```



::: {.column-body-outset}

::: {.panel-tabset .box-shadow}

## Join

##### Interested in becoming a member of AP-LS?

Please identify your membership category below and follow the instructions on our membership management page to join today!


::: {.grid}


::: {.g-col-12 .g-col-md-4}
<div class="price-card h-100">
<div class="card-body d-flex flex-column">
<div class="price-card-header">
<p class="display-2"><span class="currency">$</span>50<span class="period">/year</span></p>
</div>
<div class="price-card-block">
<h4 class="price-card-title">
        Full or Associate
      </h4>
<h5 class="price-card-subtitle">
  Individuals with degree in psych or related field: </h5>
<ul class="list-group">
  <li class="list-group-item">Doctoral Degree</li>
  <li class="list-group-item">Juris Doctorate</li>
  <li class="list-group-item">Masters Degree</li>
  <li class="list-group-item">Terminal Bachelors Degree</li>
</ul>
<a href="#" class="price-btn price-btn-gradient mt-2">Join now</a>
</div>
</div>
</div>
:::


::: {.g-col-12 .g-col-md-4}
<div class="price-card h-100">
<div class="card-body d-flex flex-column">
<div class="price-card-header">
<p class="display-2"><span class="currency">$</span>15<span class="period">/year</span></p>
</div>
<div class="price-card-block">
<h4 class="price-card-title"> Early Career </h4>
<h5 class="price-card-subtitle">
  Individuals within 10 years of receiving: </h5>
<ul class="list-group">
  <li class="list-group-item">Doctoral Degree</li>
  <li class="list-group-item">Juris Doctorate</li>
  <li class="list-group-item">Masters Degree</li>
  <li class="list-group-item">Terminal Bachelors Degree</li>
</ul>
<a href="#" class="price-btn price-btn-gradient mt-2">Join now</a>
</div>
</div>
</div>
:::

::: {.g-col-12 .g-col-md-4}
<div class="price-card h-100">
<div class="card-body d-flex flex-column">
<div class="price-card-header">
<p class="display-2"><span class="currency">$</span>15<span class="period">/year</span></p>
</div>
<div class="price-card-block">
<h4 class="price-card-title"> Student </h4>
<h5 class="price-card-subtitle">
  Individuals currently enrolled as either: </h5>
<div style="margin-top: 40px; margin-bottom: 55px;">
<ul class="list-group">
  <li class="list-group-item">Undergraduate Student</li>
  <li class="list-group-item">Graduate Student</li>
</ul>
</div>
<a href="#" class="price-btn price-btn-gradient mt-2">Join now</a>
</div>
</div>
</div>
:::

:::


## Renew

##### Did you receive a renewal notice from the AP-LS Office?

Please complete this renewal form and continue receiving member benefits with AP-LS.

<a class="btn btn-primary" href="https://apls.memberclicks.net/membership-renewal-form#!/" role="button">Renew Membership</a>

## Questions?

If you have any questions about membership, please contact the **American Psychology-Law Society**:

<p>{{< fa phone title="Phone" >}} {{< var contact.phone >}} </br> {{< fa envelope title="Email" >}} {{< var email.office >}} </br> {{< fa location-dot title="Location" >}} {{< var contact.mail >}}</p>


::: {.callout-tip collapse="true}
## Forensic Psychology Diplomat 

If you are interested in obtaining Forensic Psychology Diplomat status in the American Board of Forensic Psychology and American Board of Professional Psychology, please contact: 

ABPP </br>
600 Market Street, 
Suite 300 </br>
Chapel Hill, NC 27516 </br>
{{< fa phone >}} (919) 537-8031 </br>
{{< fa fax >}} (919) 537-8034

More information can be found on websites: [American Board of Forensic Psychology](http://www.abfp.com/) and [American Board of Professional Psychology](http://www.abpp.org/).
:::
:::

:::

# Why join AP-LS?

The American Psychology-Law Society (AP-LS) is an interdisciplinary organization devoted to scholarship, practice, and public service in psychology and law.

AP-LS is both a free-standing organization as well as a division (Division 41) of the American Psychological Association (APA). Membership in AP-LS is therefore separate and independent from membership in Division 41 of APA, although many members belong to both organizations (AP-LS and APA).

##### Members of AP-LS enjoy a variety of benefits including:

```{r echo=FALSE, message=FALSE, warning=FALSE}
#| label: benefits table
#| classes: '.g-col-lg-6 .g-col-12 .g-col-md-12'

content = rowwise_table(~icon, ~text, ~link,
          "book",
            "Online access to the official journal of AP-LS, Law and Human Behavior.", 
              "https://www.apa.org/pubs/journals/lhb/",
          "newspaper",          
            "Online subscription to the AP-LS monthly newsletter.",   
              "../publications/index.html",
          "award",          
            "Eligibility to apply for grants, fellowships, and awards.",                                 "../awards/index.html",
          "credit-card",        
            "Discounts on AP-LS conference registration.",
              "../conferences/index.html",
          "clipboard-data",      
            "Ability to vote in annual AP-LS elections.",              
              "../about/leadership.html",
          "info-circle",        
            "Access to additional resources and networking opportunties.",                   
              "../resources/index.html"
)
div(class = "feature-grid",
  pmap(content, function(icon, text, link) {
    div(class = "feature-grid__item",
        div(class="feature-grid__icon",
          a(href = link, class = "feature-grid__link",
            tags$i(class = sprintf("bi-%s feature-grid__i", icon))
         )
       ),
      text
    )
  })
)
```


# Who can join?

Membership is open to interested professionals and students in other disciplines beyond psychology. AP-LS encourages APA members, graduate and undergraduate students, and persons in related fields to consider joining.

## Membership Types

##### There are six categories of membership in AP-LS including:

```{r}
#| echo: false
content = rowwise_table(~name, ~icon, ~url, ~text,
  "Full", "person-fill",      "",                                   "Individuals with a doctoral degree (Ph.D., Psy.D., M.D., or Ed.D.) in psych or related field or a Juris Doctorate.",
    "Associate", "person-fill",      "",                                   "Inviduals with a master's degree in psych or related field or a terminal bachelors degree.",
    "Early Career", "person-fill",      "",                                   "Individuals within 10 years of receiving latest degree.",
    "Fellows", "award",      "",                                   "Individuals granted Fellow Status (Full Members) or Distinguished Member status (Full Afilliates) by the society.",
    "International", "globe", "", "Individuals who reside outside the United States with a relevant doctoral degree. All join as International Affiliates.",
  "Student",           "mortarboard-fill",  "", 
  "Individuals currently enrolled in undergraduate or graduate program. All join as Student Affiliates."
)
div(class = "grid grid-three",
  pmap(content, function(name, icon, url, text, objective) {
      div(class = "grid__item",
        h3(class = "grid__title",
          tags$i(class = sprintf("bi-%s grid__title-icon", icon)),
          span(class = "grid__title-name", name)
        ),
        p(class = "grid__text", text),
        a(href = url, span(class = "grid__link-box"))
      )
  })
)
```

For a more detailed description of each category of membership, see the [AP-LS Bylaws](../about/bylaws.html).
