---
title: "Telepsychology Resources"
date: last-modified
title-block-banner: "../../images/default-banner.svg"
categories:
  - Telepsychology
---

The American Psychology-Law Society has convened a task force that seeks, in part, to identify telepsychology resources for students, researchers, and clinicians and have these citations centrally available on our website. The following lists are intended to educate and inform practitioners and scholars in both the implementation and study of forensic telepsychology work.


APA Professional Practice Guidelines for the Practice of Telepsychology have been developed by a Joint Task Force comprised of representatives from The American Psychological Association (APA), the Association of State and Provincial Psychology Boards (ASPPB) and the APA Insurance Trust (APAIT). 


<div class="d-flex flex-wrap justify-content-start align-items-center">
  [{{< fa book-open-reader >}} APA Guidelines](https://www.apa.org/practice/guidelines/telepsychology){.btn .btn-outline-primary role="button"}
    [{{< fa file-pdf >}} AP-LS Statement & Recommendations](https://psycnet.apa.org/fulltext/2023-90234-001.html){.btn .btn-outline-primary role="button"}
</div>

::: vspace2
:::

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
#| label: new table
#| echo: false

library(readr)
library(htmltools)
library(dplyr)
library(reactablefmtr)

tele <- readr::read_csv("telepsych.csv") 

data <- tele |> 
  mutate(col_colors = case_when(
    type == 'Forensic' ~ '#4271B3',
    type == 'Non-forensic' ~ '#1B3264',
    type == 'General' ~ 'gray',
             TRUE ~ '#FBF9F4'),
    img = knitr::image_uri("link.png")
) |> 
  select(type, name, img, url, cite, col_colors)
  
tbl <- reactable(
    data,
    theme = fivethirtyeight(header_font_size = 16),
    filterable = TRUE,
    defaultColDef = colDef(
      vAlign = "center",
      headerVAlign = "bottom",
      headerClass = "header"
    ),
    columns = list(
      type = colDef(
        name = "Type",
        cell = pill_buttons(
          data,
          opacity = 0.8,
          color_ref = 'col_colors',
          text_size = 14,
      ),
        filterInput = function(values, name) {
          tags$select(
          # Set to undefined to clear the filter
          onchange = sprintf("Reactable.setFilter('cat-select', '%s', event.target.value || undefined)", name),
          # "All" has an empty value to clear the filter, and is the default option
          tags$option(value = "", "All"),
          lapply(unique(values), tags$option),
          "aria-label" = sprintf("Filter %s", name),
          style = "width: 100%; height: 28px;"
        )
        }
      ),
      name = colDef(
        filterable = FALSE,
        name = "Resource",
        minWidth = 250), 
      img = colDef(
        name = "Link",
        align = "center",
        filterable = FALSE,
        html = TRUE,
        cell = function(value, index) {
        sprintf('<a href="%s" target="_blank"><image src="%s" style="width:30px;height:30px;"/></a>', data$url[index], value)
      }
    ),
    
    cite = colDef(
      filterable = FALSE,
      name = "Citation",
      minWidth = 300
      ),
    url = colDef(show = FALSE),
    col_colors = colDef(show = FALSE)
      ),
    defaultPageSize = 10,
    elementId = "cat-select"
    )
    
tbl
```
