---
title: Distinguished Contributions to Psychology and Law
date: last-modified
description: Honors one who has made distinguished theoretical, empirical, and/or applied contributions to the field of psychology and law.
categories: 
  - Distinguished Career
submission-info:  
  sponsor: AP-LS Executive Committee
  deadline: January 1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../../assets/apls_functions.R")
```

::: vspace
:::

::: callout-note
All nominations should be sent in a single file Word or pdf format to AP-LS Past President Lora Levett at `llevett@ufl.edu` by January 1, 2023. </br> Self-nominations will not be considered.

```{r}
#| echo: false
#| output: asis

library(tibble)
library(dplyr)

# Important links for award
links <- tibble(
  icon = c("file-import"),
  text = c("Submit nomination"),
  url = c("llevett@ufl.edu")
)

# Create inline objects for each row of the tibble
inline_objects <- lapply(seq_len(nrow(links)), function(i) {
  create_inline_object(links[i, "icon"], links[i, "text"], links[i, "url"])
})

# Combine the inline object strings into a single string
inline_objects_str <- paste(inline_objects, collapse = "")

# Print the HTML string
cat(inline_objects_str)
```
:::

::: vspace
:::

::: panel-tabset
## Description

The AP-LS Award for Distinguished Contributions to Psychology and Law honors one who has made distinguished theoretical, empirical and/or applied contributions to the field of psychology and law. This award will not be presented on a regular basis. Rather, it will be reserved for those individuals whose contributions are so unusual as to merit special commendation.

## Eligibility

This award is not exclusively for AP-LS members, and anyone who meets these criteria may be nominated.

## How to Apply

All nominations should be sent in a single file Word or pdf format to AP-LS Past President Lora Levett (llevett\@ufl.edu) by January 1, 2023.

:::{.callout-tip} 
## Nominations must include:

-   A copy of the nominee's CV

-   A letter detailing the nominee's distinguished contributions to psychology and law

-   Names and addresses of four individuals who are familiar with the nominee's work and who would be able to address the nominee's contributions to the field of psychology and law (or additional letters from these four individuals).

Self-nominations will not be considered.
:::

:::
```{=html}

    <!-- Past recipients -->

<div class="accordion" id="accordionExample">
  <div class="accordion-item">
    <h2 class="accordion-header" id="headingOne">
      <button class="accordion-button" type="button" data-bs-toggle="collapse" data-bs-target="#collapseOne" aria-expanded="false" aria-controls="collapseOne">
        Past Recipients
      </button>
    </h2>
    <div id="collapseOne" class="accordion-collapse collapse" aria-labelledby="headingOne" data-bs-parent="#accordionExample" style="">
      <div class="accordion-body">  
      
      <strong>2018:</strong> James Ogloff <br>
      <strong>2017:</strong> Michael Saks <br>
      <strong>2016:</strong> Kirk Heilbrun and Chris Slobogin <br>
      <strong>2015:</strong> Gail Goodman <br>
      <strong>2014:</strong> Saul Kassin <br>
      <strong>2013:</strong> Michael E. Lamb <br>
      <strong>2012:</strong> Thomas Grisso <br>
      <strong>2011:</strong> Norman Poythress <br>
      <strong>2010:</strong> Ronald Roesch <br>
      <strong>2008:</strong> Elizabeth Loftus <br>
      <strong>2006:</strong> Stanley Brodsky <br>
      <strong>2005:</strong> Janet Reno <br>
      <strong>2001:</strong> Gary Wells <br>
      <strong>1998:</strong> Larry Wrightsman <br>
      <strong>1992:</strong> Bruce Sales <br>
      <strong>1990:</strong> Supreme Court Justice Harry Blackmun <br>
      <strong>1988:</strong> John Monahan and Laurens Walker <br>
      <strong>1986:</strong> Saleem Shah (First time awarded)
```    
      
