---
title: Outstanding Teaching and Mentoring in the Field of Psychology and Law
date: last-modified
description: Recognizes teaching and mentoring excellence in the field of psychology and law. 
categories: 
  - Teaching
  - Early Career Professionals
submission-info:
  sponsor: AP-LS Teaching, Training and Career Committee
  deadline: December 15
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../../assets/apls_functions.R")
```

::: vspace
:::

::: callout-note

## Details
Nominations should be submitted to {{< var email.ttc >}} before annual December 15 deadline.

```{r}
#| echo: false
#| output: asis
#| label: Details

library(tibble)
library(dplyr)

# Important links for award
links <- tibble(
  icon = c("circle-info", "envelope"),
  text = c("About TTC Committee", "Contact"),
  url = c("../../about/committees.html", "mailto:ttc@ap-ls.org")
)

# Create inline objects for each row of the tibble
inline_objects <- lapply(seq_len(nrow(links)), function(i) {
  create_inline_object(links[i, "icon"], links[i, "text"], links[i, "url"])
})

# Combine the inline object strings into a single string
inline_objects_str <- paste(inline_objects, collapse = "")

# Print the HTML string
cat(inline_objects_str)
```
:::

::: vspace
:::

::: panel-tabset
## Description

The American Psychology-Law Society confers an award for Outstanding Teaching and Mentoring in the Field of Psychology and Law to recognize teaching excellence in a variety of contexts.

Every year Div. 41 (American Psychology-Law Society) confers two awards for Outstanding Teaching and Mentoring in the Field of Psychology and Law to recognize teaching excellence in a variety of contexts: Outstanding Teaching and Mentoring Award and the Early Career Teaching and Mentoring Award. The winner of the awards will be announced at the annual meeting of the American Psychology-Law Society.

In even-numbered years (e.g., 2024, 2026), the award will be given to a teacher/mentor from a program/department that is undergraduate-only or MA-terminus (category 1).

In odd-numbered years (e.g., 2025, 2027), the award will be given to a teacher/mentor from a program/department that is doctoral-granting or postdoctoral granting; including law schools, medical schools, and non-university positions such as hospitals, clinics or other organizations. The primary requirement is that the recipient have taught/mentored graduate and/or postdoctoral students (category 2).

Recipients of the awards will receive \$500 and a plaque at the AP-LS conference.

## Eligibility

Nominees should be persons who have made substantial contributions to student training in the field of psychology and law.

To be eligible for the Outstanding Teaching and Mentoring Award an individual must have held a Doctoral Degree or Juris Doctorate for 11 years or more, and must have been teaching and/or mentoring students in psychology and law for 11 years or more.

To be eligible for the Early Career Teaching and Mentoring Award, an individual must have held a PhD or JD degree for 10 years or less, and must have been teaching and/or mentoring students in psychology and law for 10 years or less (i.e., AP-LS Early Career Professionals).

::: callout-note
Nominees cannot apply for both awards.
:::

## How to Apply

The nomination package should be emailed directly to {{< var email.ttc >}} before the annual December 15 deadline.

::: callout-info
## The nomination package should include:

1.  Nominee's statement (one--two pages) of teaching/mentoring philosophy, goals, and accomplishments, especially as related to the field of psychology and law (Please state which award you are applying for (Outstanding Teaching and Mentoring Award or the Early Career Teaching and Mentoring Award) and how you meet the criteria for that award.)

2.  Abbreviated curriculum vitae (three pages maximum)

3.  Summarized student evaluations; (student evaluations should be recent and include at least 3 years)

4.  At least one, but no more than three, supporting letters from peer reviewers or students

    </p>

    </li>

5.  Other relevant documentation such as descriptions of current and past student achievements; mentoring in one-on-one teaching contexts (e.g., advising, clinical supervision); teaching in the community (e.g., workshops that bring psychology and law to applied audiences); teaching-related committee work or scholarship; development of new curricula, courses, course materials or instructional methods

The total nomination packages must be no more than 15 pages total.

Self-nominations are encouraged.
:::


## Past Recipients

| Year   | Outstanding Teaching and Mentoring Award              | Early Career Award                |
|------------------------|------------------------|------------------------|
| 2023   | Angela Evans (category 2)                             | Ashley Batastini (category 2)     |
| 2022   | Dan Krauss (category 1)                               | Apryl Alexander (category 1)      |
| 2021\* | Allison Redlick (category 2)                          | Anthony Perillo (category 2)      |
| 2020   | Garrett Berman (category 1)                           | Nesa E. Wasarhaley (category 1)   |
| 2019   | Eve M. Brank and Robert E. Cochrane (category 2)      | Cynthia J. Najdowski (category 2) |
| 2018   | Jennifer L. Groscup (category 1)                      | Tess M.S. Neal (category 1)       |
| 2017   | Monica K. Miller and Jennifer Robbennolt (category 2) |                                   |
| 2016   | Matthew Huss (category 1)                             | Amanda Zelechoski (category 1)    |
| 2015   | Jodi Quas (category 2)                                |                                   |
| 2014   | Bradley D. McAuliff (category 1)                      |                                   |
| 2013   | Roderick C.L. Lindsay (category 2)                    |                                   |
| 2012   | Amye R. Warren (category 1)                           |                                   |
| 2011   | Brian Bornstein (category 2)                          |                                   |
| 2010   | Mark Costanzo (category 1)                            |                                   |
| 2009   | Ronald Roesch (category 2)                            |                                   |
| 2008   | Edie Greene (category 1)                              |                                   |
| 2007   | N. Dickson Reppucci (category 2)                      |                                   |
| 2006   | Bette Bottoms and Jim Ogloff                          |                                   |
| 2005   | Bette Bottoms and Jim Ogloff                          |                                   |
| 2004   | Margaret Bull Kovera                                  |                                   |
| 1996   | Gail Goodman (First time awarded)                     |                                   |
:::