---
title: AP-LS Award for Best Undergraduate Paper
date: last-modified
description: Recognizes an outstanding undergraduate research paper focused on the interdisciplinary study of psychology and law.
categories:
  - Students
  - Undergraduate
submission-info:
  sponsor: AP-LS Undergraduate Paper Award Committee
  deadline: "June 30, `r if (Sys.Date() > lubridate::mdy(paste('June 30', lubridate::year(Sys.Date())))) lubridate::year(Sys.Date()) + 1 else lubridate::year(Sys.Date())`"
links:
- icon: send
  name: Submit here
  url: "mailto:undergrad_paper@ap-ls.org"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../../assets/apls_functions.R")
```

<hr>

::: panel-tabset
## Description

The AP-LS Award for Best Undergraduate Paper is awarded to an outstanding undergraduate research paper that is focused on the interdisciplinary study of psychology and law.

First ($500), second ($200) and third place ($150) winners are conferred annually, and winners will be be encouraged to submit their work as a poster presentation at the AP-LS Annual Conference (as first author).

## Eligibility

To be eligible for an award the student must be the major contributor to a project on a topic relevant to psychology and law (i.e., the student had primary responsibility for initiating and conducting the project even though the project will usually be conducted under the supervision of a mentor).

Data collection should be complete.

Students may submit their work during their first post-undergraduate year as long as the work was conducted during their undergraduate career.

## How to Apply

<a class="btn btn-primary" href="mailto:undergrad_paper@ap-ls.org" role="button"><i class="fa-regular fa-file-word"></i> Submit Here</a>

Submissions (APA-paper and letter of support) must be emailed to to the Chair of the Undergraduate Paper Award Committee at `undergrad_paper@ap-ls.org` as .doc or .docx (Microsoft Word) files. Deadline for receipt of all materials is June 30.

:::{.callout-tip}
## Submission must include the following:
1.    One copy of the APA-style paper being submitted for consideration.
  -   The paper should be a maximum of 25 pages of text (12-point font, one-inch margins), including the abstract and tables/figures.
  -   The 25-page maximum does not include the title page and references.

2.   A letter of support from the student's faculty mentor.
  -   Each applicant must have their mentor submit a letter of support to the chair that characterizes the nature and extent of the student's contribution to the project.
  -   This letter should be a maximum of two pages of text (12-point font, one-inch margins).

Applications that do not meet these requirements for the paper and letters of support will be disqualified.
:::

## Proposal Review Criteria
Proposals will be reviewed by members of the AP-LS Undergraduate Paper Award Committee based on independence, originality, contribution to field, soundness of design and analyses and quality of writing.

## Past Recipients

```{r}
#| label: undergrad-winners
#| warning: false
#| echo: false
library(dplyr)
library(purrr)

# Data: awards/data/undergrad-paper.csv (refresh via awards/_update-awards.R)
data <- read.csv("../data/undergrad-paper.csv") |>
  mutate(
    rank = recode(tolower(trimws(award)),
                  first  = "1st place",
                  second = "2nd place",
                  third  = "3rd place",
                  .default = NA_character_),
    detail = pmap_chr(list(rank, affiliation, advisor), function(r, a, ad) {
      parts <- c(r,
                 if (!is.na(a)  && a  != "") a else NA,
                 if (!is.na(ad) && ad != "") paste0("advisor: ", ad) else NA)
      paste(parts[!is.na(parts) & parts != ""], collapse = " · ")
    })
  )

awards_table(data, name = "name", detail = "detail")
```
:::
