---
title: Grants-in-Aid for Graduate Students MacArthur Award
date: last-modified
description: Additional funding from the MacArthur Foundation to fund promising research in the area of criminal competence.
categories: 
  - Students
  - Graduate 
  - Research
  - Grants-in-Aid
submission-info:
  sponsor: AP-LS Graduate Grants-in-Aid Committee
  deadline: January 15 & September 15
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../../assets/apls_functions.R")
```

::: vspace
:::

::: callout-note
Applications should be submitted via the [AP-LS Awards Portal](https://awards.ap-ls.org/default.asp) before the annual October 15 deadline.  
```{r}
#| echo: false
#| output: asis

library(tibble)
library(dplyr)

# Important links for award
links <- tibble(
  icon = c("circle-info", "envelope", "link"),
  text = c("About Early Career Professionals Committee", "Contact", "Link to apply"),
  url = c("../../about/committees.qmd", "ecp@apls.org", "https://awards.ap-ls.org/default.asp")
)

# Create inline objects for each row of the tibble
inline_objects <- lapply(seq_len(nrow(links)), function(i) {
  create_inline_object(links[i, "icon"], links[i, "text"], links[i, "url"])
})

# Combine the inline object strings into a single string
inline_objects_str <- paste(inline_objects, collapse = "")

# Print the HTML string
cat(inline_objects_str)
```
:::

::: vspace
:::

:::{.panel-tabset}
## Description
The AP-LS Student Grants-in-Aid (GIA) Committee is pleased to announce the availability of additional funding from the MacArthur Foundation to fund promising research in the area of criminal competence. 

Interested applicants may submit research proposals to the GIA Committee and follow the same timeline as regular GIA applications.

## Eligibility
-   Awards are limited to research proposals addressing questions of adjudicative competence in juveniles and adults. Both "seed money" for larger projects and "stand alone" projects are acceptable.

-   Applicants may submit only one application per funding cycle, with preference afforded to those who have never been given the award previously. In rare circumstances, a second award may be given, but only if research using the previous award has been completed.

-   Underrepresented groups include but are not limited to racial and ethnic minorities, first-generation college students, LGBTQIA individuals, and students with physical disabilities. 
      
-   As with AP-LS-GIA general funding, recipients must be current members of AP-LS and should submit documentation of prior IRB approval and relevant tax forms. 

-   Although the quality of the research should be the primary determining factor in granting awards, requested budget items must be clearly specified and appropriate. With only the rarest exceptions, travel expenses would ordinarily be excluded. 
      
-   The maximum for any individual award is set at $2,000. 
-   A rejection of a particular proposal by the subcommittee does not exclude its consideration for an AP-LS-GIA award.
      
-   If a student submits an application for AP-LS-GIA involving research on adjudicative competence, the chair—at his or her discretion and with the student's written permission—may forward the application for review by the subcommittee for additional funding.

## How to Apply

Interested individuals should follow the application instructions provided on the general [Grants in Aid for Graduate Students award page]("../GRADgrantinaid.qmd").


<a class="btn btn-primary" href="https://awards.ap-ls.org/default.asp" role="button">Link to Apply</a>

Annual application deadlines are **January 15** and **September 15**
:::